Turbo fast no compromise gravitational wave parameter estimation

### 2022-12-12 src/tex/ms.tex
Add heterodyne likelihood paragraphs

\kw{Specify the idea of heterodyned likelihood here}.
The idea behind heterodyned likelihood is the following:

@@

@@

% GPU helps pack a shit ton of waveform evaluation
Another benefit accelerator brings is parallel evaluation of waveforms. The most
expensive part of evaluating the likelihood is generating the waveform. This is
especially significant when analysis long signals such as BNS merger, since the
cost of evaluating the waveform scales linearly with the number of time samples.
While the most accurate waveform model, numerical relativity, is a sequential
process, most of the gravitational wave models used in PE are approximants,
meaning they are fits to numerical relativity waveforms. These fitted form can
be evaluated at any given time or frequency without the need to simulate the
signals from an initial condition. This means generating a waveform from an
approximant can in fact be benefited from parallelization. Together with
heterodyned likelihood, we can evaluate the likelihood at $\mathcal{O}(10^7)$
different locations on an Nvidia A100 GPU. The high throughput of likelihood
evaluations unlocks the potential of the \texttt{flowMC} sampling algorithms.

@@

% Brief summary
In this work, we present a PE pipeline for GW events that is efficient and flexible.

@@

% More features such as marginalization
The features we have implemented are the barebone version of parameter
estimation. We do not include marginalization schemes such as time, phase and
calibration lines marginalization. Because of the performance of the sampler on
accelerators, time and phase marginalization is not necessary, as the
performance of our implementation is not significantly impacted by having two
extra dimension. Other marginalization mode should be considered in the future.

@@

% Multi-device scaling

% Higher dimensional problems need HMC still

>>>>

\kw{Specify the idea of heterodyned likelihood here}. The idea behind
heterodyned likelihood can be summarized as the following: the integrand in eq.
\ref{eq: innerproduct} is highly oscillatory function, so one has to sample the
integrand with sufficiently dense sampling to compute the integral faithfully.
The number of sample points needed would be much smaller if the integrand was
smooth. Given a pair of waveform parameters $\mathbf{\theta}$ and
$\mathbf{\theta_0}$ that are close to each other, the waveforms generated using
the pair of parameters are similar to each other, this means the ratio between
the waveforms is a smoothly varying function. Given a reference waveform
$h(\mathbf{\theta_0})$, we can exploit this similarity between waveforms to
reduce the number of sample points needed to compute the likelihood for the set
of $\mathbf{\theta}$ that are similar to $\mathbf{\theta_0}$. We decompose
the integrand into two parts: a highly oscillatory part that is depends only on
the reference waveform and the data, hence it only needs to be evaluated once;
and a smoothly varying part that depends on the target waveform parameters
$\theta$, that needs to be evaluated for every new likelihood evaluation.
Because the part that depends on the target waveform parameters is smooth, we
can use far fewer sample points to compute the integral with sufficient
accuracy.

@@

One may be concerned by the accuracy of this approximation over the target
parameter space, especially in the region where the generated waveform is
significantly different from the reference waveform. However, given we are
interested in the most probable set of parameters, if we choose the reference
waveform to be close to the data, the waveforms that are different from the
reference waveform should also differ significantly from the data. This means
the likelihood value for these waveforms should be significantly smaller than
the likelihood for the waveforms that are similar to the reference waveform,
hence will not be relevant for the PE result. In practice, one will first
optimize the likelihood function with full frequnecy resolution to obtain the
reference waveform parameters, which can be run at a much lower cost compared to
PE.

@@

% GPU helps pack a shit ton of waveform evaluation
Another benefit accelerator brings is parallel evaluation of waveforms. Since
the waveform models being used in PE are approximants, they can be evaluated at
any given time or frequency independent to what have been generated before the
time or frequency. This means predicting the waveform can be trivially
parallelized over frequency. Together with heterodyned likelihood, we can
evaluate the likelihood at $\mathcal{O}(10^7)$ different locations on an Nvidia
A100 GPU. The high throughput of likelihood evaluations unlocks the potential of
the \texttt{flowMC} sampling algorithms.

@@

% Brief summary
In this work, we present a PE pipeline for GW events that is efficient and
flexible. With a differentiable waveform model, heterodyned likelihood and
normalizing flow enhanced sampler \texttt{flowMC}, we are able to estimate the
parameters of GW150914 and GW170817 in \kw{Quote speed}. Our method is general
and extensable, \kw{continue}.

@@

In order to perform realistic PE with our pipeline, the detector pattern o
The current code can perform parameter estimation for any combination of the
Hanford, Livingston and Virgo detectors, under the assumption of

% More features such as marginalization
The features we have implemented are the barebone version of parameter
estimation. We do not include marginalization schemes such as time, phase and
calibration lines marginalization. Because of the reaonsable performance of the sampler on
accelerators, time and phase marginalization is not necessary, as the
performance of our implementation is not significantly impacted by having two
extra dimension. Other marginalization mode should be considered in the future.

@@

% Interplay with importance sampling

% Multi-device scaling
The current implementation take
